---
title: "Vintereksamen - Dataanalyse"
subtitle: "Januar 2023"
date: last-modified
author: "Claus Grand Bang, Anna Hald Refsgaard og Bjarne Taulo Sørensen"
format: 
  pdf:
   toc: true
   toc-title: Indholdsfortegnelse
   toc-depth: 4
   number-sections: true
   number-depth: 3
   geometry:
      - top=30mm
      - left=20mm
      - right=20mm
      - bottom=30mm
      - heightrounded
    
abstract: "Her kan I skrive et abstract, som ikke bør fylde mere end en halv side. Bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, bla, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa, blaaaa......"
---

```{r}
#| label: setup
#| include: false

# eval: false prevents code from being evaluated. (And obviously if the code is not run, no results will be generated). This is useful for displaying example code, or for disabling a large block of code without commenting each line.

# include: false runs the code, but doesn’t show the code or results in the final document. Use this for setup code that you don’t want cluttering your report.

# echo: false prevents code, but not the results from appearing in the finished file. Use this when writing reports aimed at people who don’t want to see the underlying R code.

# Du kan lave code chunks med crtl/alt/I. 
# Angiv en label som ovenfor til hver chunk. 
# Brug evt. include, eval, echo til at få det ønskede output_column
```

```{r}
pacman::p_load("tidyverse", "magrittr", "nycflights13", "gapminder","Lahman", "maps",
"lubridate", "pryr", "hms", "hexbin", "feather", "htmlwidgets",
"broom", "pander", "modelr", "XML", "httr", "jsonlite", "lubridate", "microbenchmark", "splines", "ISLR2", "MASS", "testthat", "leaps", "caret", "RSQLite", "class", "babynames", "nasaweather", "fueleconomy", "viridis", "readxl", "timeDate", "tinytex","ggbeeswarm", "palmerpenguins", "hms")
```
Indlæser datasæt: Halløjsa. 
```{r}
data1 <- read_excel("data/stud_exam_data.xlsx") 
```




```{r}
dsfsdfdsfsdffsdfsdf
```

# Intro 

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Oversigt

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

# Metode

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Videnskabsteori

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

# Databrug (intern analyse i data perspektiv)

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Organisation

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Processer (benchmark)

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Kultur

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Modenhed

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.## Systemer

# Datainitiativer

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Introduktion til dataanalysen

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Baggrund

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Formål

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Fra fortningsproblem til datamining problem

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Oversigt

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Data/dataforståelse

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Importer data til R

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Output variabel

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Forklarende variabler

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Data pre-processing i R

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Explorative analyse

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Vurdering af outliers

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Vurdering af missing værdier

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Transformationer af variabler

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

# Valg af metode til at teste model performance

## Resultater

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Konkurrerende modeller

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Modeludvælgelse

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Endelig model

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Overordnet præcision i forudsigelse

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Observeret og prædiktet værdier af målvariablen

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Forbedring i forhold til en baseline model (ingen model)

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

#### Prædiktion med selv-konstruerede forklarende variabler

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

## Diskussion

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Vurdering af modellens performance

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Vurdering af bidraget til løsningen af forretningsproblemet

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

### Udrulning af anbefalingerne

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.

<!-- ## Foreslå opfølgningsaktiviteter -->

# Konklusion

Quarto supports executable code blocks within markdown allowing you to create fully reproducible documents and reports. The code required to produce your output is part of the document itself, and is automatically re-run whenever the document is rendered.
